Surrogate Modelling of the Tritium Breeding Ratio

### 2020-06-21 talk_ucl_cdt_200622/adaptive.tex
removed duplicate slide
Data generation slide updated.
Adaptive update

        Adaptive sampling takes advantage of surrogate information content \textit{during training} to reduce sample quantity.\newline

@@

    $60\%$ decrease in MAE for independent evaluation (dashed lines) \newline
    Equivalently, $6\%$ decrease in samples needed for same accuracy

>>>>

        How can we take advantage of surrogate information content \textit{during training} to reduce sample quantity?\newline

@@

\end{frame}
1
